### 2024-06-01 2024-5-13/sections/heuristic.tex
fix some mistakes in heuristic

\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $(\snum_2(e)$ and $\rnum_2(e))$. 
%
\item From the construction in Section~\ref{sec:algorithm}, 
two NFAs $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters. As a result, the alphabets of $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively. The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$. Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$. Similarly for $\cU_{\aut_{\ufld_1(e)}}$. 
Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
%
\item If $sz_1 \le sz_2$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
\end{itemize}

>>>>

\item We estimate the sizes of the two CEFAs $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ constructed from $\ufld_1(e), \ufld_2(e)$ respectively as pairs $(\snum_1(e), \rnum_1(e))$ and $(\snum_2(e), \rnum_2(e))$, where $\snum_1(e)$ and $\rnum_1(e)$ are the estimates of the number of states and registers in $\aut_{\ufld_1(e)}$, similarly for $\snum_2(e)$ and $\rnum_2(e)$. 
%
\item From the construction in Section~\ref{sec:algorithm}, 
two NFAs $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are constructed from $\aut_{\ufld_1(e)}$ and $\aut_{\ufld_2(e)}$ by dropping the accepting conditions and ignoring the characters. As a result, the alphabets of $\cU_{\aut_{\ufld_2(e)}}, \cU_{\aut_{\ufld_2(e)}}$ are the set of integer vectors  $\myvec{v}$ occurring in the transitions of $\aut_{\ufld_1(e)}, \aut_{\ufld_2(e)}$ respectively. The integer vectors of  $\aut_{\ufld_1(e)}$ are of form $(\underbrace{0, \cdots, 0}_{i-1}, 1, \underbrace{0, \cdots, 0}_{r'-i-1})$, where $i \in [r']$. Consequently, the size of the alphabet of $\cU_{\aut_{\ufld_1(e)}}$ is bounded by $\rnum_1(e)$. Similarly for $\cU_{\aut_{\ufld_1(e)}}$. 
Finally, we estimate the sizes (number of transitions) of the NFAs $\cU_{\aut_{\ufld_1(e)}}, \cU_{\aut_{\ufld_2(e)}}$ as $sz_1 = (\snum_1(e))^2 \cdot \rnum_1(e)$ and $sz_2 = (\snum_2(e))^2 \cdot \rnum_2(e)$ respectively.
%
\item If $sz_1 \le sz_2$, then we choose to unfold the counting operators in $e_1$. Otherwise, we choose to unfold the counting operator $^{\{m,n\}}$. 
\end{itemize}
